---
title: "Reviewercomments_explicitdataonly_accuracy"
author: "Jaskanwaljeet Kaur"
date: "4/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Loading libraries:
```{r}
library(lme4)
library(broom)
library(ggplot2)
library(magrittr)
library(dplyr)
library(tidyverse)
library(optimx)
library(parallel)
library(minqa)
library(report)
library(ggExtra)
library(ggstatsplot)
library(sjmisc)
library(emmeans)
library(hausekeep)
library(lmerTest)
library(standardize)
```
#We'll start by importing the explicit learning condition accuracy dataset:
```{r}
setwd("~/Desktop/Test SRT")
explicit_data_acc <- read.csv("EL_Accuracy_data_for_analysis.csv")
explicit_data_acc
```
#Let's center the data by substracting the mean:
```{r}
explicit_data_acc$block_centered.c <- explicit_data_acc$Block_number - mean(explicit_data_acc$Block_number)
print(explicit_data_acc)
```
#Let's seperate the explicit learning data above into two datasets (training - AV and testing AO) so we can add a few things before modeling them:
```{r}
explicit_data_acc_split <- split(explicit_data_acc, explicit_data_acc$Part_Type)

AV_data_acc <- explicit_data_acc_split$`Audio+Video`
print(AV_data_acc)

A0_data_acc <- explicit_data_acc_split$`Audio Only`
print(A0_data_acc)
```
#We're going to get rid of the catch trials here and so that only the sequential trials remain in the explicit (AV-training) dataset:
```{r}
#This data gets rid of the catch trial rows in the dataset:
AV_data_seq <- AV_data_acc[!(AV_data_acc$Block_number_num == "1_AV" | AV_data_acc$Block_number_num == "6_AV"| AV_data_acc$Block_number_num == "ten_AV"),]
print(AV_data_seq)

AV_data_seq <- AV_data_seq %>%
  mutate(trialtype = "Sequential")
AV_data_seq
```
#Here we're going to get rid of the sequential trials so that we are left with catch trials only:
```{r}
AV_data_catch <- AV_data_acc[!(AV_data_acc$Block_number_num == "2_AV" | AV_data_acc$Block_number_num == "3_AV" | AV_data_acc$Block_number_num == "4_AV" | AV_data_acc$Block_number_num == "5_AV"| AV_data_acc$Block_number_num == "7_AV"| AV_data_acc$Block_number_num == "8_AV" | AV_data_acc$Block_number_num == "9_AV"),]
print(AV_data_catch)

AV_data_catch <- AV_data_catch %>%
  mutate(trialtype = "Catch")
AV_data_catch
```
#Here we bind together the AV (training dataset) now that we have names the sequential and the catch trials:
```{r}
AV_data_acc_seq_catch <- rbind(AV_data_seq, AV_data_catch)
print(AV_data_acc_seq_catch)
```
#Next, we're going to create a model using ONLY the AV data. This data also include sequential vs. random trials. This model should tell us the following: The sequential data is significantly different than the random/catch data.
```{r}
training_AV_model_only <- lmer(accuracy_int ~ trialtype + (1 | participant_id), data = AV_data_acc_seq_catch)

report(training_AV_model_only)
#emmeans to look at the three way interaction (pair-wise interactions; plot this as well.)
summary(training_AV_model_only)
#summaryh(training_AV_model_only)

plot(training_AV_model_only)
#Checking normality of residuals either via:
#A Q-Q plot 
qqnorm(resid(training_AV_model_only))
qqline(resid(training_AV_model_only))
#Or a histogram of residuals:
hist(residuals(training_AV_model_only))
```
```{r}
full_model_training <- lmer(accuracy_int ~ trialtype + (1 | participant_id), data = AV_data_acc_seq_catch)
model_training <- lmer(accuracy_int ~ 1 + (1 | participant_id), data = AV_data_acc_seq_catch)

anova(full_model_training,model_training)
```

```{r}
library(sjPlot)
sjPlot::plot_model(training_AV_model_only, show.values = TRUE, value.offset = .3, vline.color = "yellow", title = "Reaction Time Estimates", sort.est = TRUE)
```
```{r}
sjPlot:: tab_model(training_AV_model_only,
                   dv.labels= "Log Tranformed Reaction Time")
```

#A0 model analysis:
```{r}
A0_data_acc <- explicit_data_acc_split$`Audio Only`
print(A0_data_acc)
```
```{r}
#This data gets rid of the catch trial rows in the dataset:
A0_data_seq <- A0_data_acc[!(A0_data_acc$Block_number_num == "1_A" | A0_data_acc$Block_number_num == "6_A"| A0_data_acc$Block_number_num == "ten_A"),]
print(A0_data_seq)

A0_data_seq <- A0_data_seq %>%
  mutate(trialtype = "Sequential")
A0_data_seq
```
```{r}
A0_data_catch <- A0_data_acc[!(A0_data_acc$Block_number_num == "2_A" | A0_data_acc$Block_number_num == "3_A" | A0_data_acc$Block_number_num == "4_A" | A0_data_acc$Block_number_num == "5_A"| A0_data_acc$Block_number_num == "7_A"| A0_data_acc$Block_number_num == "8_A" | A0_data_acc$Block_number_num == "9_A"),]
print(A0_data_catch)

A0_data_catch <- A0_data_catch %>%
  mutate(trialtype = "Catch")
A0_data_catch
```
```{r}
A0_data_seq_catch <- rbind(A0_data_seq, A0_data_catch)
print(A0_data_seq_catch)
```
```{r}
testing_AO_model_only <- lmer(accuracy_int ~ trialtype + (1 | participant_id), data = A0_data_seq_catch)

report(testing_AO_model_only)
#emmeans to look at the three way interaction (pair-wise interactions; plot this as well.)
summary(testing_AO_model_only)
#summaryh(training_AV_model_only)

plot(testing_AO_model_only)
#Checking normality of residuals either via:
#A Q-Q plot 
qqnorm(resid(testing_AO_model_only))
qqline(resid(testing_AO_model_only))
#Or a histogram of residuals:
hist(residuals(testing_AO_model_only))
```
```{r}
full_model_training_AO <- lmer(accuracy_int ~ trialtype + (1 | participant_id), data = A0_data_seq_catch)
model1_training_AO <- lmer(accuracy_int ~ 1 + (1 | participant_id), data = A0_data_seq_catch)

anova(full_model_training_AO,model1_training_AO)
```
```{r}
library(sjPlot)
sjPlot::plot_model(testing_AO_model_only, show.values = TRUE, value.offset = .3, vline.color = "yellow", title = "Reaction Time Estimates", sort.est = TRUE)
```

```{r}
sjPlot:: tab_model(testing_AO_model_only,
                   dv.labels= "Log Tranformed Reaction Time")
```

